Adding Interactivity to Static Rmarkdown Documents

### 2017-11-19 02_rmarkdown-interactivity/post.Rmd
More progress

**Plot Data**

@@

hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "static_graph") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_chart(height = 500) %>%
  hc_xAxis(title = list(text = "Value")) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities") %>% 
  hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")

@@

# Preparing Data

@@

Now we'll create those 6 key javascript arrays.

@@

# In action

```{r}
hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "interactive_graph") %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities")

@@

>>>>

## Plot Data

@@

hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "static_graph") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_chart(height = 500) %>%
  hc_xAxis(title = list(text = "Value")) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "Probability Densities: Uniform, Normal, and Exponential") %>% 
  hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")

@@

## Preparing Data

@@

Now we'll use both of those functions to create our 6 key javascript arrays.

@@

## The Javascript

Now what we have to do is write some - relatively simple - javascript to switch CDF and PDF data when the user presses a button.

The key things to call out in this code are:
* thing 1
* The `show_cdf` boolean keeps track of which view to switch out
* To find the `highcharts` object within the page you can use the `.highcharts()`
* More things

## In Action

Now let's see why we went to all that effort.

hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "interactive_graph") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(title = list(text = "Value")) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "Probability Distributions: Uniform, Normal, and Exponential") %>% 
  hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")

@@

<br>
<br>
